Vision-Based Automatic Landing of Drones

### 2024-10-21 Article/Article.tex
Add Algorithm design and Future work sections

        \author[a]{Adi Peisach}
        \ead{adi.peisach@gmail.com}

@@

        \begin{abstract}
            This article introduces a platform designed to enable precise landings on the edge of rooftops, facilitating operations at boundary locations. The platform integrates voice recognition capabilities for activation, eliminating reliance on manual button controls. The primary objective is to develop a methodology and control algorithm that allows drones to guard settlements effectively. This research employs a combination of straight-line detection and object detection, avoiding the use of global positioning systems. The system is engineered to operate with drones equipped with existing cameras, obviating the need for additional sensors, and is implemented using the DJI SDK on Android devices. This paper presents a visual landing technology through a proposed algorithm, which is divided into two key tasks: scene evaluation and landing site security. Initially, the drone utilizes object detection to identify and avoid obstacles within the landing area, enabling autonomous descent planning. Once obstacles are cleared, the drone transitions to descent mode. For precise landings at the edge of a rooftop, an edge detection algorithm is employed alongside a target line selection process, allowing the user to designate a specific landing line beforehand, ensuring accuracy during the final approach.

        \end{abstract}

@@

    \subsection{Authors Contribution}
    We propose a visual processing framework that enables the drone to autonomously land by utilizing object (obstacle) detection and edge detection. Our approach is tested on a DJI drone equipped with a standard camera, using the DJI SDK for implementation on Android devices. Additionally, we have implemented a "guard" mode in the app—a button that, when activated, is designed to detect movement (such as people, cars, etc.) and send alerts. The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.

    \begin{figure}[htp]
        \centering
        \includegraphics[width=11.0cm]{Schematic_for_automatic_landing.png}
        \caption{Schematic for automatic landing.}
        \label{fig:Schematic_for_automatic_landing.}
    \end{figure}
    \\

% \subsection{Paper Structure}
% This paper is structured as follows: Section \ref{sec:related} discusses related work in autonomous drone landing and visual navigation. Section \ref{sec:datasets} details the datasets used for testing and validation. Section \ref{sec:framework} describes the proposed framework, including the algorithms and implementation details. Section \ref{sec:exp_eval} presents the experimental evaluation and results. Finally, Section \ref{sec:discussion} offers a discussion on the findings, and Section \ref{sec:conclusions} concludes the paper with suggestions for future work.

% \begin{table}[th]
%   \caption{List of abbreviations}

%   \centering
%   \begin{tabular}{ |c|c|c|}
%   \hline
%     \multicolumn{1}{|c|}{\textbf{Abbreviation}} &
%     \multicolumn{1}{|c|}{\textbf{Meaning}}\\\hline
%     PID & \quad Proportional Integral Derivative \\\hline

%   \end{tabular}
%   \label{tab:list_of_abbreviations}
% \end{table}

@@

    \subsection{An improved Canny edge detection algorithm}
    Edge detection algorithms play a critical role in enhancing the visual processing capabilities of drones by accurately identifying boundaries and objects within an image. The Canny Edge Detection Algorithm, as discussed in \cite{rong2014improved}, has proven to be highly effective due to its ability to detect edges with minimal noise while maintaining high accuracy. This method ensures that drones can detect and track obstacles, aiding in precise navigation and autonomous landing. Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.
% \cite{lee2022camera} is a set.

% Spoken language recognition (SLR) has been a

% \section{Datasets} \label{sec:datasets}

% In the field of speech recognition, the ability to accurately transcribe

    \section{Drone Control Mechanisms} \label{sec:framework}
    The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
    \begin{description}
        \item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
        \item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
        \item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
        \item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
    \end{description}
    //Maybe add more? about the remote also?

    \section{Framework} \label{sec:framework}
    \subsection{Speech Recognition}
    The speech recognition system continuously listens for voice commands, enabling real-time control of the drone without touching the screen. \\
    Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
    \begin{description}
        \item $\bullet$ Takeoff - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
        \item $\bullet$ Land - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
        \item $\bullet$ Stop - Halts any current movement, keeping the drone stationary in hover mode.
        \item $\bullet$ Move up - Increases the throttle to elevate the drone vertically.
        \item $\bullet$ Move down - Decreases the throttle, causing the drone to descend.
        \item $\bullet$ Start recording - Begins video recording using the drone's camera.
        \item $\bullet$ Stop recording - Stops the video recording and saves the footage.
        \item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.

@@

    \section{Experimental Evaluation and Results} \label{sec:exp_eval}

    In accordance with the methodologies outlined in the framework, several modifications were independently evaluated. Below is a tabulated comparison illustrating the differences among these variations, as in Table~\ref{tab:results_comparison}:

    \begin{table}[ht]
        \centering
        \caption{Comparative Analysis of Model Improvements on Validation Dataset.}
        \label{tab:results_comparison}
        \resizebox{0.4\textwidth}{!}{%
            \begin{tabular}{|c|c|}
                \hline
                \textbf{Model} & \textbf{Accuracy} \\
                \hline
                Baseline & 0.54 \\

                \hline
            \end{tabular}%
        }
    \end{table}

    Figure~\ref{fig:conf_matrix_test} depicting the confusion matrices for the final model on :

    \begin{figure}[htp]
        \centering
        \includegraphics[width=11.0cm]{con_matrix_test.jpeg}
        \caption{Confusion Matrix on Validation Dataset for the Final Model, showing minimal error.}
        \label{fig:conf_matrix_test}
    \end{figure}

    The results in Eq.(\ref{eq:inequality}) clearly demonstrate that Boaz has no idea in equations.

    \begin{equation} \label{eq:inequality}
    3 \neq 3
    \end{equation}

@@

    \section{Conclusions and Future Work} \label{sec:conclusions}

    In this study, we have

>>>>

% \author[a]{Adi Peisach}
% \ead{adi.peisach@gmail.com}

@@

\begin{abstract}
This article introduces a platform designed to enable precise landings on the edge of rooftops, facilitating operations at boundary locations. The platform integrates voice recognition capabilities for activation, eliminating reliance on manual button controls. The primary objective is to develop a methodology and control algorithm that allows drones to guard settlements effectively. This research employs a combination of straight-line detection and object detection, avoiding the use of global positioning systems. The system is engineered to operate with drones equipped with existing cameras, obviating the need for additional sensors, and is implemented using the DJI SDK on Android devices. This paper presents a visual landing technology through a proposed algorithm, which is divided into two key tasks: scene evaluation and landing site security. Initially, the drone utilizes object detection to identify and avoid obstacles within the landing area, enabling autonomous descent planning. Once obstacles are cleared, the drone transitions to descent mode. For precise landings at the edge of a rooftop, an edge detection algorithm is employed alongside a target line selection process, allowing the user to designate a specific landing line beforehand, ensuring accuracy during the final approach.
\end{abstract}

@@

\subsection{Authors Contribution}
We propose a visual processing framework that enables the drone to autonomously land by utilizing object (obstacle) detection and edge detection. Our approach is tested on a DJI drone equipped with a standard camera, using the DJI SDK for implementation on Android devices. Additionally, we have implemented a "guard" mode in the app — a button that, when activated, is designed to detect movement (such as people, cars, etc.) and send alerts. The system's robustness is further enhanced by incorporating basic voice commands through a speech recognition module, meeting the requirements outlined by MAFAT.\\

\newpage \section{Algorithm Design} \label{sec:algorithm}
Our proposed algorithm for autonomous drone landing consists of three key components: Target Line Selection, Flight Control, and Object Detection. Each part contributes to the overall reliability and precision of the landing process, ensuring safe navigation and obstacle avoidance.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\textwidth]{Schematic_for_automatic_landing.png}  % Reduced the size here
    \caption{Schematic for automatic landing.}
    \label{fig:Schematic_for_automatic_landing.}
\end{figure}

\subsection{Target Line Selection}
In the first stage of the landing process, edge detection is activated to identify all available and compatible lines within the camera's field of view. These lines represent potential landing paths. The user interacts with the system by selecting the desired line for the drone to land behind via a touch-based interface. Once the target line is chosen, the algorithm continuously tracks the line. This is achieved by calculating the distance between the selected line and all detected lines, and the one with the minimum distance is updated as the current target line. This real-time tracking ensures that the drone can maintain accurate navigation towards the desired landing area.

\subsection{Flight Control}
After target line selection, the system activates the flight control module. The drone begins moving towards the selected line by issuing pitch commands, which direct forward movement. This continues until the chosen line is nearly out of the drone’s visible range. Through experimental measurements, we identified a blind spot between the drone's final visible position of the line and its actual location in reality. To compensate for this, the algorithm calculates the necessary adjustment and issues a final pitch command, ensuring that the drone reaches the correct position relative to the target line.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\textwidth]{Blind Spot Area.png}  % Reduced the size here
    % \caption{Schematic for automatic landing.}
    \label{fig:Blind Spot Area.}
\end{figure}

\subsection{Object Detection}
Upon reaching the target area, object detection is initiated to scan for potential hazards in the intended landing zone. The detection algorithm examines the area for obstacles such as people, vehicles, or other objects that may hinder safe landing. The landing zone's dimensions are calculated based on prior measurements from different drone positions, ensuring the detection area is appropriately scaled for accurate hazard identification. If no hazards are detected, the system proceeds with the landing sequence, ensuring a safe and precise touchdown.

@@

\subsection{An improved Canny edge detection algorithm}
Edge detection algorithms play a critical role in enhancing the visual processing capabilities of drones by accurately identifying boundaries and objects within an image. The Canny Edge Detection Algorithm, as discussed in \cite{rong2014improved}, has proven to be highly effective due to its ability to detect edges with minimal noise while maintaining high accuracy. This method ensures that drones can detect and track obstacles, aiding in precise navigation and autonomous landing. Its application in real-time drone systems highlights its importance in improving the robustness of visual navigation and obstacle avoidance.

\section{Drone Control Mechanisms} \label{sec:framework}
The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
\begin{description}
\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
\end{description}

\section{Framework} \label{sec:framework}
\subsection{Speech Recognition}
The speech recognition system, powered by Google Speech Recognition, continuously listens for the user’s voice until it detects the wake word "hey rexi." Once activated, the system checks subsequent speech for commands from the predefined list, enabling real-time control of the drone without touching the screen. This approach allows the system to remain responsive while minimizing unnecessary processing, facilitating a hands-free operation experience.

Each recognized command triggers a specific action in the drone. The key commands and their associated actions are:
\begin{description}
\item $\bullet$ Takeoff - Initiates the drone's takeoff sequence, lifting it to a designated altitude for hover.
\item $\bullet$ Land - Initiates the landing sequence, lowering the throttle for a controlled descent until the drone reaches the ground.
\item $\bullet$ Stop - Halts any current movement, keeping the drone stationary in hover mode.
\item $\bullet$ Move up - Increases the throttle to elevate the drone vertically.
\item $\bullet$ Move down - Decreases the throttle, causing the drone to descend.
\item $\bullet$ Start recording - Begins video recording using the drone's camera.
\item $\bullet$ Stop recording - Stops the video recording and saves the footage.
\item $\bullet$ Edge detection - Activates the edge detection algorithm, allowing the system to identify and process edges for navigation or object tracking.

@@

@@

\newpage \section{Future Work} \label{sec:future}
An important area for future improvement is the algorithm's ability to handle wind conditions, particularly in outdoor environments and at higher altitudes. While the current implementation performs reliably in controlled settings, real-world scenarios—such as fluctuating wind speeds and changing directions—pose significant challenges to the drone's stability and landing accuracy. Specifically, turbulence at great heights can disrupt the drone's trajectory, leading to deviations from the intended flight path and reducing the precision of both target line tracking and landing position.

To address these challenges, we plan to enhance the algorithm by integrating real-time wind compensation techniques. This improvement will involve adapting the flight control module to account for external forces, using sensor and visual data to counteract wind disturbances, and dynamically adjusting the drone's movements. Enhancing wind handling will enable the algorithm to perform more reliably across a wider range of scenarios, ensuring consistent operation in varying environmental conditions.

Additional future work includes transitioning the speech recognition system from an online to an offline model, which will improve reliability by ensuring consistent functionality without internet access. Furthermore, we plan to explore the integration of plane recognition algorithms to enhance landing precision. This capability will enable the drone to autonomously identify suitable landing surfaces, thus increasing safety and operational efficiency.

\section{Conclusion}
